Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-06 aistats.tex
Rename file and add \hypersetup{draft} to avoid fatal error

\documentclass[twoside]{article}
\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%\usepackage[accepted]{aistats2022}

@@

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\graphicspath{{../figs/}{../}}
%\usepackage{subfigure}
\usepackage{subcaption}
\usepackage{hyperref}       % hyperlinks
\usepackage[dvipsnames]{xcolor}

@@

% my packages
\usepackage{../math_commands}
% some custom math commands
\newtheorem{proposition}{Proposition}
\newcommand*{\expect}[2][]{\ensuremath{\mathbb{E}_{#1} \left[ #2 \right] }} % expectation operator
\newcommand{\cond}{\,\vert\,}
\newcommand{\logpart}{A}
\newcommand{\conj}{\logpart^*}
\newcommand{\bregman}{\cB_\logpart}
\newcommand{\bregmanconj}{\cB_{\logpart^*}}
\newcommand{\natp}{\theta}
\newcommand{\meanp}{\mu}
\newcommand{\decrement}{D}
\newcommand{\linear}{\ell} % linearization of a function
\newcommand{\lr}{\gamma} % learning rate, or step-size
\newcommand{\lin}[1]{\left\langle#1\right\rangle}

@@

@@

There is a long line work trying the convergence rate of stochastic gradient descent.
Beyond the results of RM51, 
we now have proofs n smooth, strongly convex problems and bounded variance 
(as well as other assumptions on the noise, reviewed later)
a decreasing step-size and an averaging scheme gets 
a $1/t$ convergence rate, 
which matches the asymptotic rate of unbiased estimation,
through clever averaging schemes \citep{rakhlin2012making,lacostejulien2012simpler}\footnote{
Those papers assume the stochastic gradients are bounded, 
but small modifications also work for bounded variance instead.
}

@@

\fdk{
Application

The problems on how to deal with Bregman divergences abound in optimization, beyond stochasticity. 
For example, we haven't yet figured out the analog of Nesterov-type acceleration 
on relatively smooth and strongly convex problems, 
to bring the convergence rate from linear in $(1-\kappa)$ to $(1-\sqrt{\kappa})$, 
or just from $1/T$ to $1/T^2$ 
in the (non-strongly) convex case.
\citet{dragomir2021optimal} show that naïve application of Bregman updates can not achieve acceleration.
The tools developped to make progress on one problem might help make progress on the other. 
}

\bibliographystyle{apalike}
\bibliography{../references.bib}

>>>>

\documentclass[twoside]{article}
\usepackage{aistats/aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%\usepackage[accepted]{aistats2022}

@@

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\graphicspath{{figs/}}
%\usepackage{subfigure}
\usepackage{subcaption}
\usepackage{hyperref}       % hyperlinks
\usepackage[dvipsnames]{xcolor}

@@

% my packages
\usepackage{math_commands}
% some custom math commands
\newtheorem{proposition}{Proposition}
\newcommand*{\expect}[2][]{\ensuremath{\mathbb{E}_{#1} \left[ #2 \right] }} % expectation operator
\newcommand{\cond}{\,\vert\,}
\newcommand{\logpart}{A}
\newcommand{\conj}{\logpart^*}
\newcommand{\bregman}{\cB_\logpart}
\newcommand{\bregmanconj}{\cB_{\logpart^*}}
\newcommand{\natp}{\theta}
\newcommand{\meanp}{\mu}
\newcommand{\decrement}{D}
\newcommand{\linear}{\ell} % linearization of a function
\newcommand{\lr}{\gamma} % learning rate, or step-size
\newcommand{\lin}[1]{\left\langle#1\right\rangle}

@@

\hypersetup{draft}

@@

There is a long line work trying the convergence rate of stochastic gradient descent.
Beyond the results of RM51, 
we now have proofs n smooth, strongly convex problems and bounded variance 
(as well as other assumptions on the noise, reviewed later)
a decreasing step-size and an averaging scheme gets 
a $1/t$ convergence rate, 
which matches the asymptotic rate of unbiased estimation,
through clever averaging schemes \citep{rakhlin2012making,lacostejulien2012simpler} \footnote{
Those papers assume the stochastic gradients are bounded, 
but small modifications also work for bounded variance instead.
}

@@

ff
\fdk{Application 
The problems on how to deal with Bregman divergences abound in optimization, beyond stochasticity. 
For example, we haven't yet figured out the analog of Nesterov-type acceleration 
on relatively smooth and strongly convex problems, 
to bring the convergence rate from linear in $(1-\kappa)$ to $(1-\sqrt{\kappa})$, 
or just from $1/T$ to $1/T^2$ in the (non-strongly) convex case.
}

\citet{dragomir2021optimal}  shows that naïve application of Bregman updates can not achieve acceleration.
The tools developed to make progress on one problem might help make progress on the other.

\bibliographystyle{apalike}
\bibliography{references.bib}
